Estimating individual subjective values of emotion regulation strategies

### 2023-01-13 06_Paper/ER-ED/ERED_Stage2/Manuscript_ERED_Stage2.Rmd
updated workspace load

# load workspace variables from analyses_ERED.R script
load(here("06_Paper","ER-ED","ERED_Stage2","Workspace_ERED_pilot.RData"))

>>>>

# load workspace variables from analyses_ERED.R script
base::load(here("06_Paper","ER-ED","ERED_Stage2","Workspace_ERED_pilot.RData"))
base::load(here("06_Paper","ER-ED","ERED_Stage2","Workspace_ERED.RData"))
